---
title: "Eating Out"
author: "Cesar Guillen"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

There is about no difference between the black and other race from how many times they eat out, but the white race seem to eat out more than both the black and other races. About 80% of the white people asked said they do eat out, where as 65% of black people who were asked if they eat out said yes they do. 


```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

With the tables above we can see that the white population are the race that is eating out the most than the other and black races. We can see that in both tables a little above 80 percent of white people eat out, and that the white population makes up more than 80 percent of the total of people who said yes. For the black race we see that 69 percent of them say that they do eat out once per week, but they only make up 11 percent of the total population who were asked and said yes. And finally we see that the other races category has 72 percent that said yes to eating out, but they only make 6 percent of the total population that said yes. We can say that this was most likley swerewed to asking more white people than other races. 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```



